---
title: "R Code for Dissertation Chapter 5"
author: "Kristi Gdanetz MacCready"
output: html_document
---
*** 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Set-up

```{r, eval=FALSE}

### Load packages and data --------------------------------
library(readxl)
library(ggplot2)
library(plyr)

conidia_counts <- read_excel("~/Documents/conidia_counts.xlsx")

View(conidia_counts)
```

## Generate summary statistics 
This creates an new table that will be used to for the graph
```{r, eval=FALSE}

cdata <- ddply(conidia_counts, c("Strain", "Timepoint"), summarise,
               N    = sum(!is.na(Cells_mL)),
               Avg = mean(Cells_mL, na.rm=TRUE),
               StDev   = sd(Cells_mL, na.rm=FALSE),
               StErr   = (StDev/(sqrt(N)))) 
View(cdata)
```

## Generate the plot
```{r, eval=FALSE}

ggplot(data = cdata, #plot data points
       aes(x = Timepoint, y = Avg,
           group = Strain, color = Strain)) + 
  geom_line(size=1) + geom_point(size = 3) +  #add line
  geom_errorbar(aes(ymin=Avg-StErr, ymax=Avg+StErr), #add error bars
                width=0.2) +
  scale_x_discrete("Time (hours)", #manually set axes
                   labels = c("0", "24", "48", "72", "96", "120")) + 
  scale_y_continuous(seq(0, 30000000, 7500000), 
                     name = "Concentration (conidia/ml)") +
  theme(panel.grid.minor.y=element_blank(), #clean up background
        panel.grid.major.y=element_blank(),
        panel.grid.minor.x=element_blank(),
        panel.grid.major.x=element_blank()) +
  scale_color_manual(values = c("#faa51a", "#9bca3c", "#70c6a5", #set colors
                                "#426fb6", "#8750a0", "#ed187a")) +
  scale_fill_manual(breaks=c("PH1","2B","3B"), #set legend order
                    labels=c("PH1","2B","3B"))

```

Plot generated should look like this:  

![](/Users/Home/Documents/Google_Drive/Research/Terpene_Synthase/conidia_plot.tiff)

*** 

## Test for significance 
Use ANOVA and post-hoc test to determine if concentrations are significantly different between time points. 

```{r, eval=FALSE}

```

